---
title: "R Notebook"
output:
  html_document:
    df_print: paged
    code_folding: show
---

# Diagrama de causalidad

```{r}
#install.packages('dagitty')

library(dagitty)
g1 <- dagitty('dag{
"Cámara" [pos="0,1"]
"Atención" [pos="1,0"]
"Dinamismo" [pos="1,1"]
"Conexión" [pos="1,2"]
"Aprendizaje" [pos="2,1"]
"Cámara" -> "Atención" -> "Aprendizaje"
"Cámara" -> "Dinamismo" -> "Aprendizaje"
"Cámara" -> "Conexión" -> "Aprendizaje"
"Dinamismo" -> "Atención"
}')

plot(g1)

```

### Agregamos nueva variable
```{r}
g3 <- dagitty('dag{
"Cámara" [pos="0,1"]
"Atención" [pos="1,0.5"]
"Dinamismo" [pos="1,0"]
"Conexión" [pos="1,1"]
"Aprendizaje" [pos="2,1"]
"Privacidad" [pos="0.5,1.5"]
"Participación" [pos="1,2"]
"Cámara" -> "Atención" -> "Aprendizaje"
"Cámara" -> "Dinamismo" -> "Aprendizaje"
"Cámara" -> "Conexión" -> "Aprendizaje"
"Cámara" -> "Privacidad" -> "Participación" -> "Aprendizaje"
"Dinamismo" -> "Atención"
"Conexión" -> "Participación"
}')

plot(g3)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

## Damos formato

```{r}
# install.packages('ggdag')
library(ggplot2)
library(ggdag)



```

## Hilo de relaciones

¿Quién causa el efecto en aprendizaje directamente?

Resto de variables que causan
```{r}
parents(g3,"Aprendizaje")

ancestors(g3,"Aprendizaje")

children(g3,"Cámara")

descendants(g3,"Cámara")
```
# Prueba FETS

```{r}
#install.packages('Matching')
#install.packages('EnvStats')

library(Matching)
library(EnvStats)
data(lalonde)
attach(lalonde)

x <- re78[treat==1]/1000
y <- re78[treat==0]/1000

twoSamplePermutationTestLocation(x,y,alternative="two.sided", seed=123)

```
# Prueba de Neyman

```{r}
yiT <- re78[treat==1]/1000
yiC <- re78[treat==0]/1000
myiT <- mean(yiT)
myiC <- mean(yiC)

(tau <- abs(myiT - myiC))

(vartau <- var(re78[treat==1]/1000)/length(yiT)+
var(re78[treat==0]/1000)/length(yiC))

(tstat <- tau/sqrt(vartau))

2*(1-pnorm(tstat))
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}


```